Cross-Validation Default

### 2024-01-31 minos/validation/cross_validation_default.Rmd

## Household Size

@@

## Housing Tenure

@@

@@

%## Job Sec
%
%```{r}
%jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
%                                          df1.name = 'simulated', 
%                                          df2 = raw, 
%                                          df2.name = 'raw', 
%                                          var = 'job_sec')
%
%cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
%                 var = 'job_sec',
%                 save = FALSE)
%rm(jobsec.pivoted)
%```
%
%## Hourly Wage
%
%```{r}
%cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
%multi_year_boxplots(raw, cv, 'hourly_wage')
%q_q_comparison(raw, cv, 'hourly_wage')
%```

@@

## CHILDREN AGEING

@@

# CHILD POVERTY VARS

## Relative Poverty

```{r}
relative_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'relative_poverty')

cv_ordinal_plots(pivoted.df = relative_poverty.pivoted, 
                 var = 'relative_poverty',
                 save = FALSE)
rm(relative_poverty.pivoted)
```

## Absolute Poverty

```{r}
absolute_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                   df1.name = 'simulated', 
                                                   df2 = raw, 
                                                   df2.name = 'raw', 
                                                   var = 'absolute_poverty')

cv_ordinal_plots(pivoted.df = absolute_poverty.pivoted, 
                 var = 'absolute_poverty',
                 save = FALSE)
rm(absolute_poverty.pivoted)
```

## Material Deprivation

```{r}
matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                               df1.name = 'simulated', 
                                               df2 = raw, 
                                               df2.name = 'raw', 
                                               var = 'matdep_child')

cv_ordinal_plots(pivoted.df = matdep_child.pivoted, 
                 var = 'matdep_child',
                 save = FALSE)
rm(matdep_child.pivoted)
```

## Low Income and Material Deprivation

```{r}
low_income_matdep_child.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                          df1.name = 'simulated', 
                                                          df2 = raw, 
                                                          df2.name = 'raw', 
                                                          var = 'low_income_matdep_child')

cv_ordinal_plots(pivoted.df = low_income_matdep_child.pivoted, 
                 var = 'low_income_matdep_child',
                 save = FALSE)
rm(low_income_matdep_child.pivoted)
```

## Persistent Poverty

```{r}
persistent_poverty.pivoted <- combine_and_pivot_long(df1 = cv, 
                                                     df1.name = 'simulated', 
                                                     df2 = raw, 
                                                     df2.name = 'raw', 
                                                     var = 'persistent_poverty')

cv_ordinal_plots(pivoted.df = persistent_poverty.pivoted, 
                 var = 'persistent_poverty',
                 save = FALSE)
rm(persistent_poverty.pivoted)
```

>>>>

## hhsize

@@

## housing tenure

@@

## nkids Household

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'nkids')
multi_year_boxplots(raw, cv, 'nkids')
q_q_comparison(raw, cv, 'nkids')
```

## nkids Max

```{r}
raw.nkids_max <- raw %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'final_US')

cv.nkids_max <- cv %>%
  dplyr::select(pidp, time, nkids) %>%
  group_by(time) %>%
  summarise(max_nkids = max(nkids)) %>%
  mutate(source = 'baseline_output')

multi_year_boxplots(raw.nkids_max, cv.nkids_max, 'max_nkids')
```

@@

## Job Sec

```{r}
jobsec.pivoted <- combine_and_pivot_long(df1 = cv, 
                                          df1.name = 'simulated', 
                                          df2 = raw, 
                                          df2.name = 'raw', 
                                          var = 'job_sec')

cv_ordinal_plots(pivoted.df = jobsec.pivoted, 
                 var = 'job_sec',
                 save = FALSE)
rm(jobsec.pivoted)
```

## Hourly Wage

```{r}
cv.mean.plots(cv1, cv2, cv3, cv4, cv5, raw, 'hourly_wage')
multi_year_boxplots(raw, cv, 'hourly_wage')
q_q_comparison(raw, cv, 'hourly_wage')
```

@@

@@
